Appendix to 'cubble: An R Package for Organizing and Wrangling Multivariate Spatio-temporal Data

### 2022-07-09 jss/appendix.Rmd
use library("foo") style as suggested by JSS

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(tidyverse)
library(cubble)
library(patchwork)
library(leaflet)
library(leafpop)
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library("tidyverse")
library("cubble")
library("patchwork")
library("leaflet")
library("leafpop")
```
